\Huge \textcolor{titleTextColor}{ \textsf{\textbf{ \fontsize{85}{60}\selectfont GRASS GIS: a peer-reviewed scientific platform and future research repository }} }

### 2015-03-31 grassposter/2015_EGU_G7_PeerReview_SciPlatform/poster.tex
2015_EGU_G7_PeerReview_SciPlatform poster: fire Europe img added + caption (to be shortened) (provided by M Di Leo)
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64961 15284696-431f-4ddb-bdfa-cd5b030d7da7

\begin{minipage}{0.5\linewidth}
%\includegraphics[width=\textwidth]{fire}
% TODO: Something from Europe
\end{minipage}
}

>>>>

\begin{minipage}{0.5\linewidth}
\includegraphics[width=\textwidth]{fire_valencia_040914}
(Figure after Di Leo et al. 2013). The event in the figure refers to a major wildfire occurred near Valencia on June 28th 2012 and was under control on July 4th. The case study is based on a Semantic Array Programming (SemAP) application of the Dynamic Data Driven Application Systems (DDDAS) concept. The case study is based on a new architecture for adaptive and robust modelling of wildfire behaviour. It focuses on the module for simulating wildfire dynamics under fire control scenarios. Uncertainty is assessed by ensembling an array of simulations which consider the uncertainty in meteorology, fuel, software modules. 
To illustrate, simplistic fire control scenarios are shown: low wetting (top); mid-low wetting (middle) and mid-high wetting (bottom). Interpolation
driven uncertainty (IDU) is also assessed. Meteorological forecasts have been spatially disaggregated by either imposing local average invariance (LAI) (left) or not (usual non-LAI disaggregation).
\end{minipage}
}
